Mitigating Interest Flooding DDoS Attacks in NDN

### 2012-12-18 04a-design-naive.tex
more updates to sec 4a - naive strategies
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@888 df1a90cd-247b-4364-bdaf-287a704eb499

>>>>

The key drawback of the {\it Token Bucket} as well as variations of the {\it Token Bucket} algorithm that rely on fair queuing on a per-interface basis is that they still admit Interst packets from malicious users. A sizeable percentage of these malicious Interests are forwarded all the way to content producers, thereby utilizing scarce network resources and reducing resources available to serve legitimate users.  These algorithms attempt to ensure that each interface does not forward more than its fair share of Interests and in doing so they drop both legitimate Interests as well as malicious Interests. Any effective DDoS  mitigation strategy must be able to detect and effectively drop only malicious requests for content. Good Interests from legitimate users must be admited and forwarded appropriately. The key question is how can we devise mitigation algorithms that allows a router to distinguish between good and bad Interests?

Unlike in today's host-based Internet architecture where DDoS mitigation techniques that rely on blacklisting of dark IP prefixes or whitelisting of good IP prefixes are still reasonably effective, in NDN one cannot easily distinguish a 'good' prefix from a 'bad' one. Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets -- thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation. Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the name alone -- DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.

{\it Priya: Need some text massaging here so it naturally leads to the intelligent algos}

### 2012-12-18 algos/fair-queueing.tex
more updates to sec 4a - naive strategies
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@888 df1a90cd-247b-4364-bdaf-287a704eb499

As we show in Section~\ref{sec:evaluation}, fair queueing provides partial relief from the Interest flooding attack, allowing legitimate users to successfully fetch Data for 15--20\% of the expressed Interests (compared to 0-10\% without fair queueing). While these might be reasonable techniques for preventing congestion in the network and for ensuring fairness, they are far from being effective in protecting legitimate users from malicious attackers. Malicious attackers by sending a relatively small volume of Interests are able to successfully impact services for legitimate users.

The fundamental drawback of the {\it Token Bucket} as well as the fair queuing on a per-interface basis is that they fail to distinguish between good Interests from bad ones. Unlike in today's host-based Internet architecture where DDoS mitigation techniques that rely on blacklisting of dark IP prefixes or whitelisting of good IP prefixes are still reasonably effective, in NDN one cannot easily distinguish a 'good' prefix from a 'bad' one. Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets -- thus, any  Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation. Thus any DDoS mitigation technique that relies on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective. 
{\it Priya: Need some text massaging here so it flows well and naturally leads to the intelligent schemes}

>>>>

As we show in Section~\ref{sec:evaluation}, fair queueing provides partial relief from the Interest flooding attack, allowing legitimate users to successfully fetch Data for 15--20\% of the expressed Interests (compared to 0-10\% without fair queueing). While these might be reasonable techniques for preventing congestion in the network and for ensuring fairness, they are far from being effective in protecting legitimate users from malicious attackers. Malicious attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of Interests.
